### 2019-03-05 papers/icfp/3-abstractions.tex
Move the ICFP paper into a separate folder

\vspace{-1.5mm}
\subsection{Common vocabulary for build systems}\label{sec-vocabulary}
\vspace{-0.5mm}

@@

\subsection{The Task abstraction}\label{sec-task}

@@

\subsection{The Build abstraction}\label{sec-general-build}

@@

\subsection{The need for polymorphism in \hs{Task}}\label{sec-why-polymorphism}
\vspace{-0.5mm}

@@

\vspace{-0.5mm}
\subsection{Monadic tasks}\label{sec-task-monad}

@@

\subsection{Correctness of a build system}\label{sec-build-correctness}

@@

\subsection{Computing dependencies}\label{sec-deps}\label{secdeps}

>>>>

\vspace{-1.5mm}
\subsection{Common Vocabulary for Build Systems}\label{sec-vocabulary}
\vspace{-0.5mm}

@@

\subsection{The Task Abstraction}\label{sec-task}

@@

\subsection{The Build Abstraction}\label{sec-general-build}

@@

\subsection{The Need for Polymorphism in Task}\label{sec-why-polymorphism}
\vspace{-0.5mm}

@@

\vspace{-0.5mm}
\subsection{Monadic Tasks}\label{sec-task-monad}

@@

\subsection{Correctness of a Build System}\label{sec-build-correctness}

@@

\subsection{Computing Dependencies}\label{sec-deps}\label{secdeps}

### 2019-03-05 papers/icfp/5-implementations.tex
Move the ICFP paper into a separate folder

\begin{figure}
\begin{minted}[fontsize=\small]{haskell}
-- Make build system; stores current time and file modification times
type Time       = Integer
type MakeInfo k = (Time, Map k Time)
\end{minted}
\vspace{0mm}
\begin{minted}[fontsize=\small]{haskell}
make :: Ord k => Build Applicative (MakeInfo k) k v
make = topological modTimeRebuilder
\end{minted}
\vspace{0mm}
\begin{minted}[fontsize=\small]{haskell}
-- A task rebuilder based on file modification times
modTimeRebuilder :: Ord k => Rebuilder Applicative (MakeInfo k) k v
modTimeRebuilder key value task = Task $ \fetch -> do
    (now, modTimes) <- get
    let dirty = case Map.lookup key modTimes of
            Nothing -> True
            time -> any (\d -> Map.lookup d modTimes > time) (dependencies task)
    if not dirty then return value else do
        put (now + 1, Map.insert key now modTimes)
        run task fetch
\end{minted}
\vspace{0mm}
\begin{minted}[fontsize=\small]{haskell}
-- A topological task scheduler
topological :: Ord k => Scheduler Applicative i i k v
topological rebuilder tasks target = execState $ mapM_ build order
  where
    build :: k -> State (Store i k v) ()
    build key = case tasks key of
        Nothing -> return ()
        Just task -> do
            store <- get
            let value = getValue key store
                newTask :: Task (MonadState i) k v
                newTask = rebuilder key value task
                fetch :: k -> State i v
                fetch k = return (getValue k store)
            newValue <- liftStore (run newTask fetch)
            modify $ putValue key newValue
    order = topSort (graph dep target)
    dep k = case tasks k of { Nothing -> []; Just task -> dependencies task }
\end{minted}
\vspace{0mm}
\begin{minted}[fontsize=\small]{haskell}
-- Standard graph algorithms (implementation omitted)
reachable :: Ord k => (k -> [k]) -> k -> Graph k
topSort   :: Ord k => Graph k -> [k] -- Throws error on a cyclic graph
\end{minted}
\vspace{0mm}
\begin{minted}[fontsize=\small]{haskell}
-- Expand the scope of visibility of a stateful computation
liftStore :: State i a -> State (Store i k v) a
liftStore x = do
    (a, newInfo) <- gets (runState x . getInfo)
    modify (putInfo newInfo)
    return a
\end{minted}
\vspace{-3mm}
\caption{An implementation of \Make using our framework.}\label{fig-make-implementation}
\vspace{-5mm}
\end{figure}

>>>>

\begin{figure}
\begin{minted}[fontsize=\small]{haskell}
-- Make build system; stores current time and file modification times
type Time       = Integer
type MakeInfo k = (Time, Map k Time)
\end{minted}
\vspace{0mm}
\begin{minted}[fontsize=\small]{haskell}
make :: Ord k => Build Applicative (MakeInfo k) k v
make = topological modTimeRebuilder
\end{minted}
\vspace{0mm}
\begin{minted}[fontsize=\small]{haskell}
-- A task rebuilder based on file modification times
modTimeRebuilder :: Ord k => Rebuilder Applicative (MakeInfo k) k v
modTimeRebuilder key value task = Task $ \fetch -> do
    (now, modTimes) <- get
    let dirty = case Map.lookup key modTimes of
            Nothing -> True
            time -> any (\d -> Map.lookup d modTimes > time) (dependencies task)
    if not dirty then return value else do
        put (now + 1, Map.insert key now modTimes)
        run task fetch
\end{minted}
\vspace{0mm}
\begin{minted}[fontsize=\small]{haskell}
-- A topological task scheduler
topological :: Ord k => Scheduler Applicative i i k v
topological rebuilder tasks target = execState $ mapM_ build order
  where
    build :: k -> State (Store i k v) ()
    build key = case tasks key of
        Nothing -> return ()
        Just task -> do
            store <- get
            let value = getValue key store
                newTask :: Task (MonadState i) k v
                newTask = rebuilder key value task
                fetch :: k -> State i v
                fetch k = return (getValue k store)
            newValue <- liftStore (run newTask fetch)
            modify $ putValue key newValue
    order = topSort (reachable dep target)
    dep k = case tasks k of { Nothing -> []; Just task -> dependencies task }
\end{minted}
\vspace{0mm}
\begin{minted}[fontsize=\small]{haskell}
-- Standard graph algorithms (implementation omitted)
reachable :: Ord k => (k -> [k]) -> k -> Graph k
topSort   :: Ord k => Graph k -> [k] -- Throws error on a cyclic graph
\end{minted}
\vspace{0mm}
\begin{minted}[fontsize=\small]{haskell}
-- Expand the scope of visibility of a stateful computation
liftStore :: State i a -> State (Store i k v) a
liftStore x = do
    (a, newInfo) <- gets (runState x . getInfo)
    modify (putInfo newInfo)
    return a
\end{minted}
\vspace{-3mm}
\caption{An implementation of \Make using our framework.}\label{fig-make-implementation}
\vspace{-5mm}
\end{figure}
